HBots

### 2020-12-21 HBtos/article/articleHBots.tex
anadiendo cambios a las tablas mejoradas

>>>>

    \subsection*{Hockey-Stick Identity}
    \begin{center}
        \begin{tikzpicture}

            \path   (5,4) node (a) [circle,draw,] {1}
                    (4,3) node (b) [circle,draw,fill = blue] {1}
                    (6,3) node (c) [circle,draw,] {1}
                    (3,2) node (d) [circle,draw,] {1}
                    (5,2) node (e) [circle,draw,fill = blue] {2}
                    (7,2) node (f) [circle,draw,] {1}
                    (2,1) node (g) [circle,draw,] {1}
                    (4,1) node (h) [circle,draw,] {3}
                    (6,1) node (i) [circle,draw,fill = blue] {3}
                    (8,1) node (j) [circle,draw,] {1}
                    (1,0) node (k) [circle,draw,] {1}
                    (3,0) node (l) [circle,draw,] {4}
                    (5,0) node (m) [circle,draw,fill = red] {6}
                    (7,0) node (n) [circle,draw,] {2}
                    (9,0) node (o) [circle,draw,] {1};
